### 2017-06-15 paper.tex
First commit

\documentclass[oneside, 10pt]{amsart}
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, geometry, verbatim, enumitem, graphicx, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[breaklinks=true]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
%\usepackage[notref,notcite]{showkeys}
\usepackage[matrix,arrow,curve]{xy}
\usepackage[toc,page]{appendix}

\addbibresource{paper.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{http://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, thesis]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}

%\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label={\rm(\arabic{lemlisti})}, ref=\thelemma.(\arabic{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}

\theoremstyle{plain}

\newtheorem{thm}{Theorem}
\newtheorem{prop}{Proposition}
\Crefname{thm}{Theorem}{Theorems}
%\numberwithin{equation}{section}

\newtheorem{lemma}{Lemma}
%\numberwithin{lemma}{section}
\Crefname{lemma}{Lemma}{Lemmas}

\newtheorem{cor}[lemma]{Corollary}
\Crefname{cor}{Corollary}{Corollaries}

\Crefname{prop}{Proposition}{Propositions}

\newtheorem*{thm*}{Theorem}
\newtheorem*{lemma*}{Lemma}

\theoremstyle{remark}

\newtheorem{rem}[lemma]{Remark}
\Crefname{rem}{Remark}{Remarks}

\theoremstyle{definition}

\newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}

\newcommand\SmallMatrix[1]{{%
  \tiny\arraycolsep=0.3\arraycolsep\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}}
\DeclareMathOperator{\St}{St}
\DeclareMathOperator{\E}{E}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\K}{K_2}
\newcommand{\Kmw}{K^{\mathrm{MW}}_2}

\title{$\K$ of Kac---Moody groups, revisited}
\author {Sergey Sinchuk}
\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
\email {sinchukss at gmail.com}
\date {\today}

\begin{document}   
\begin{abstract} We compute $\K$-group associated to any Kac---Moody group over a field.
 The key ingredient in the computation is a variant of Smith normal form of an integer matrix.
\end{abstract}

\maketitle
%\section{Introduction}
Let $A$ be an indecomposable generalized Cartan matrix and $F$ a field.
The aim of this note is to finish the computation of the unstable $\K$-group $\K(A, F)$ started by M.~Westaway in~\cite{MW}.
Recall from~\cite{MR}, \cite{Ti} that the group $\K(A, F)$ is defined as the kernel of the map 
 $\St(A, F) \to G(A, F)$ between the corresponding Steinberg and Tits' Kac---Moody groups over $F$.

In~\cite{MR} J.~Morita and U.~Rehmann described $\K(A, F)$ as a certain quotient of abelian groups, see~\cref{thm:mr} below. 
This description allows one to immediately compute $\K(A, F)$ in the case when $A$ is finite or affine (see Corollaries~4--5 of \cite{MR}).

For general $A$, however, this description does not lead to an immediate answer and certain computation remains to be done.
In~\cite{MW} this computation was made for {\it hyperbolic} GCMs, a subclass of GCMs of indefinite type. 
Westaway's proof involved case-by-case analysis and, moreover, 
 relied on the classification of hyperbolic GCMs previously obtained by L.~Carbone et al.

In this note we describe a solution of the general problem, namely we describe an algorithm for computing $\K(A, F)$ for arbitrary $A$.
We also reprove some of the results of~\cite{MW} in a simplified form.
Our algorithm is, essentially, a variant of the well-known algorithm for computing Smith normal form of a matrix.
We also show~\cite[Conjecture 9.1]{MW} to be false as stated, and propose a way to corrected its statement.

\section{Proof of the main result}
Throughout this note $F$ denotes an arbitrary field and $A=(a_{ij})$ a generalized Cartan matrix of size $n$.
Denote by $M_A$ the subgroup of the free abelian group $\ZZ^n = \ZZ e_1 \oplus \ldots \oplus \ZZ e_n $ generated by all 
 linear combinations of the form $a_{ji} e_i - a_{ij} e_j$, $1\leq i<j\leq n$.
Set $G_A = \ZZ^n/M_A$.

Let us first recall the precise statement of the result of Morita and Rehmann.
Denote by $L_i$ either the Milnor group $\K(F)$ or the Milnor---Witt group $\Kmw(F)$ 
 depending on whether or not there exists $1 \leq k \leq n$ such that the matrix coefficient $a_{ki}$ is odd.
In either case we denote the Steinberg symbols (resp. cocycles) generating the group $L_i$ by $\{x,y\}_i$, $x, y\in F^\times$
 (see~\cite[Proposition~5.5, Lemme~5.6]{Ma} for the definition of Steinberg cocycles and symbols, respectively).
We always use additive notation for abelian groups $\K(F)$ or $\Kmw(F)$.

\begin{thm}[Morita---Rehmann] \label{thm:mr} 
 $\K(A, F)$ is isomorphic to the quotient $L/J$ where $L = L_1 \oplus L_2 \oplus \ldots \oplus L_n$ and 
 $J$ is the subgroup of $L$ generated by relators $\{x, y^{a_{ji}}\}_i - \{x^{a_{ij}}, y\}_j = 0$.
\end{thm}

Now, let us recall how $\K(A, F)$ can be computed in the special case when each column of $A$ contains an odd entry.
The following result is proved in~\cite{MW} (cf.~Theorem~5.1]).
\begin{thm} \label{thm-odd}
  Assume that every column of $A$ contains an odd entry. Assume, moreover, that
  $G_A \cong \mathbb{Z}/r_1\mathbb{Z} \oplus \ldots \oplus \mathbb{Z}/r_s\mathbb{Z} \oplus \mathbb{Z}^{n-s}\text{ for some } r_i | r_{i+1}.$
  Then 
  \begin{equation} \label{thm-eq}
    \K(A, F) \cong \frac{\K(F)}{r_1 \K(F)} \oplus \ldots \oplus \frac{\K(F)}{r_s \K(F)} \oplus \K(F)^{n-s}.
  \end{equation}
\end{thm}
\begin{proof}
 Notice that $\{x, y^k\}_i = \{x^k, y\}_i = k\{x,y\}_i$ for all $k$ and $1\leq i\leq n$.

 We already know by~\cref{thm:mr} that $\K(A, F)$ is the quotient of the abelian group 
  $\K(F)^n \cong \K(F) \otimes_{\mathbb{Z}} (\mathbb{Z}e_1 \oplus \ldots \oplus \mathbb{Z}e_n)$ by the subgroup
  \[\langle a_{ji}\{u, v\}_i - a_{ij}\{u, v\}_j \rangle \cong \langle \{u, v\} \otimes (a_{ji} e_i - a_{ij} e_j)\rangle = \K(F) \otimes M_A. \]
 Since $\{u, v\}$ generate $\K(F)$ we get $\K(A, F) \cong \K(F) \otimes (\mathbb{Z}^n / M_A) = \K(F) \otimes G_A$,
  the latter expression coincides with the expression in the right-hand side of~\eqref{thm-eq}. 
\end{proof}

Of course, the integers $r_i$ can be concretely obtained as the 
  the diagonal coefficients in the Smith normal form of the $\frac{n(n-1)}{2}\times n$ matrix $\widetilde{A}$ given by
\begin{equation} \label{eq:Aijk} \widetilde{A}_{i<j, k} = \left\{\def\arraystretch{1.2}%
  \begin{array}{@{}c@{\quad}l@{}}
     a_{ij} & \text{ for } k = i, \\
    -a_{ji} & \text{ for } k = j, \\
    0 & \text{otherwise.}    
  \end{array}\right.\end{equation}                    
Notice that the integer $s$ from the statement of~\cref{thm-odd} is precisely the number of nonzero $r_i$'s.

In the case when all entries of $A$ are even, the coefficients $r_i$ are even as well and the group $\K(A, F)$ can be computed just as easily.
%Compare the following result with~\cite[Theorem~6.1]{MW}, which is its special case.
\begin{thm} \label{thm-even}
  Assume that all entries of $A$ are even.
  Assume, moreover, that $G_A \cong \ZZ / r_1 \ZZ \oplus \ldots \oplus \ZZ / r_s\ZZ \oplus \ZZ^{m-s}$ for some $r_i$ satisfying $r_i | r_{i+1}$.
  Then
   \[\K(A, F) \cong \frac{\Kmw(F)}{(r_1/2) I} \oplus \ldots \oplus \frac{\Kmw(F)}{(r_s/2) I} \oplus \Kmw(F)^{m-s}, \]
    where $I$ denotes the subgroup of $\Kmw(F)$ generated by $\{x^2, y\}$, $x, y\in F^\times$.
\end{thm}
\begin{proof}
 Recall from ~\cite[Lemma~3.2]{MW} that
 \[\{x, y^{2k}\}_i = \{x^{2k}, y\}_i = k\{x,y^2\}_i = k\{x^2, y\}_i \text{ for all } k\text{ and } 1\leq i\leq n.\]
 By~\cref{thm:mr} the group $\K(A, F)$ is the quotient of
  $\Kmw(F) \otimes \ZZ^n$ by the subgroup 
  \[\left\langle \frac{a_{ji}}{2}\{x^2, y\}_i - \frac{a_{ij}}{2}\{x^2, y\}_j \right\rangle \cong \left\langle 
   \{x^2, y\} \otimes \left(\frac{a_{ji}}{2} e_i - \frac{a_{ij}}{2} e_j\right)\right\rangle,\ x,y\in F^\times. \]
 Thus we get that $\K(A, F) \cong \left(\Kmw(F) \otimes \ZZ^n\right) / (I \otimes M_A/2),$ as claimed. 
\end{proof}
Notice that \cite[Theorem~6.1]{MW} formally follows from the above theorem.

Now we turn to the case when $A$ contains columns of both types 
(i.\,e. there are columns having an odd entry, and consisting only of even entries).
The basic idea remains the same: we need to find a nice basis for the subgroup $J\leq L$ of defining relations of $\K(A, F)$.
This time, however, the situation is more tricky since we cannot simply tensor out $\K(F)$ or $\Kmw(F)$.
To solve the problem we need to invent some analogue of the fundamental theorem of finitely-generated abelian groups suitable to our sitation.
%We solve the problem have to keep track of its columns' ``parities''.

We need to introduce the notion of a {\it matrix with parity}.
By definition, it is simply a pair $(b, p_b)$ consisting of an integer $m\times n$ matrix $b$ and a column function $p_b\colon \{1,\ldots,n\}\to \{odd, even\}$,
 such that entries $b_{ij}$ are even for all $i$ given $p_b(j)=even$.
We call function $p_b$ a {\it parity function}.
We also call the corresponding column $b_{*i}$ {\it odd} or {\it even} depending on the value of $p_b(i)$.
%With this notation a matrix with parity is simply a matrix whose even columns consist of even entries.
Notice that we make no assumptions about entries of odd columns.

We now list five types of elementary operations that can be applied to a $m \times n$ matrix with parity $(b, p_b)$.
Later we will see that it is possible to bring a matrix with parity to Smith normal form using these operations.
\begin{enumerate}
 \item \label{item:type1} Arbitrary row operation, i.\,e. the operation that changes $b$ into $gb$ for some $g \in \E(m, \ZZ)$;
 \item \label{item:type2} Interchanging $i$-th and $j$-th columns of $b$ 
  (the corresponding values $p_b(i)$ and $p_b(j)$ of the parity function are also interchanged);
 \item \label{item:type3} Adding a multiple of a column to another column of the same parity;
 \item \label{item:type4} Adding a multiple of an even column to an odd column;
 \item \label{item:type5} Adding an even multiple of an odd column to an even column.
\end{enumerate}
All operations except the one of type~\eqref{item:type2} leave the parity function $p_b$ unchanged.
Operations \eqref{item:type3}--\eqref{item:type5} change $b$ into $bt_{ij}(\xi)$
 for some elementary transvection matrix $t_{ij}(k)$, $1\leq i\neq j\leq n$, $k \in \ZZ$.
Notice that the matrix produced by any of the above transformations is still a matrix with parity.

It is clear how matrix $\widetilde{A}$ can be reinterpreted as a matrix with parity.
Indeed, set $p_{\widetilde{A}}(i) = odd$ (resp. $p_{\widetilde{A}}(i) = even$) if the column $a_{*i}$ of
 $A$ contains an odd entry (resp. consists only of even entries).

Now let $(c, p_c)$ be an $m\times n$ matrix with parity.
Define abelian group $L(p_c)$ as the direct sum $L_1 \oplus \ldots \oplus L_n$, where 
\[L_i=\left\{\def\arraystretch{1.2}%
  \begin{array}{@{}c@{\quad}l@{}}
     \K(F) & \text{if $p_c(i) = odd$,} \\    
     \Kmw(F) & \text{if $p_c(i) = even$}.
  \end{array}\right.\]
As before, we use notation $\{u, v\}_i$ for the Steinberg symbol (or cocycle) of $i$-th summand $L_i$.
We associate to $i$-th row $c_{i*}$ of $c$ the following element of $L(p_c)$:
\[r_{c,i}(u, v) = \{ u^{c_{i1}}, v\}_1 + \ldots + \{u^{c_{in}}, v\}_{n},\ \ u, v\in F^\times.\]
Define $J(c)$ to be the subgroup of $L(p_c)$ generated by $r_{c, i}(u, v)$ for $1\leq i\leq m$, $u, v\in F^\times.$
It is clear that $L(p_c)$ and $J({\widetilde{A}})$ coincide with $L$ and $J$ from the statement of~\cref{thm:mr}.

\begin{lemma} \label{lm:inv} The isomorphism class of the quotient $L(p_c)/J(c)$ is not changed
 by any of the above five elementary transformations of $(c, p_c)$. \end{lemma}
\begin{proof}
 %Assertion of the lemma is not immediately obvious only for operations of type \eqref{item:type4} and \eqref{item:type5}. 
 Let us verify the assertion of the lemma, for example, for the operation of type~\eqref{item:type5}
  (for other operations it is similar but easier).
 Assume that $c'$ is the matrix obtained from $c$ by applying operation of type~\eqref{item:type5}.

 To verify the assertion of the lemma it suffices to show that $J(c')$ is the image of $J(c)$ under an automorphism of $L(p_c)$.
 Speaking in terms of bases, it suffices to describe how the ``new'' symbols $\{u, v\}_i'$ corresponding to $c'$ 
  are expressed in terms of ``old'' symbols $\{u, v\}_i$ corresponding to $c$.

 By assumption, $c' = c \cdot t_{ij}(2k)$ for some $i$, $j$ satisfying $p_c(i)=odd$, $p_c(j)=even$.
 This operations corresponds to the following change of basis of $L(p_c)$:
 \[ \{u, v\}_{i}^{'} = \{u, v\}_i - 2k\{u, v\}_j;\ \ \{u, v\}_{j}^{'} = \{u, v\}_j.\]
 It remains to see that $\{u, v\}_{i}^{'}$ is a Steinberg symbol.
 Although $\{u, v\}_j$ is merely a cocycle, $2k\{u, v\}_j = \{u^{2k}, v\}_j$ is a symbol (cf.~\cite[Lemma~3.2(vii)]{MW}).
 Since $\{u, v\}_{i}^{'}$ is a linear combination of symbols, it is a symbol as well.
\end{proof}

\begin{lemma} \label{lm:normal-form} Any $m \times n$ integer matrix with parity $(c, p_c)$ can be transformed into a diagonal matrix $(d, p_d)$
  ($d = \mathrm{diag}(r_1, \ldots r_{\mathrm{min}(m, n)})$, $r_i | r_{i+1}$)
   by means of elementary operations of types~\eqref{item:type1}--\eqref{item:type5}.
\end{lemma}
\begin{proof} 
Recall that one of the working steps of the classical algorithm for finding Smith normal form involves
 addition of one of the two fixed columns (say, $i$-th and $j$-th ones) to another
 so that, unless it was zero from the start, the minimum of $|c_{ki}|$ and $|c_{kj}|$ decreases strictly 
 (here $k$ is some row number and $i$, $j$ are some column numbers selected by the algorithm on one if its steps).

To adapt the classical algorithm to the situation of matrices with parities it suffices to describe
 how the modified algorithm performs the same operation in the case when the selected columns have different parities.
Indeed, the our elementary operations differ from the usual ones only in that they do not allow adding odd multiples of odd columns to even columns.

Suppose that $i$-th column of $c$ is odd and $j$-th one is even.

In the case $|c_{ki}| \geq |c_{kj}|$, write $c_{ki} + q c_{kj} = r$ for some $q$ and $r$, satisfying $|r| < |c_{kj}|$.
Using an operation of type~\eqref{item:type4} we add $q \cdot c_{*j}$ to $c_{*i}$ so that $\min(|c_{ki}|, |c_{kj}|)$ indeed decreases strictly.

In the case $|c_{ki}| < |c_{kj}|$, write $c_{kj} + q c_{ki} = r$ for some $q$ and $r$, satisfying $|r| < |c_{ki}|$.
If $q$ is even, we use an operation of type~\eqref{item:type5} to add $q \cdot c_{*i}$ to $c_{*j}$ and we are done again.
Otherwise, we can choose even $q'$ equal to either $q-1$ or $q+1$ so that one of the following is true:
\begin{itemize}
 \item $r\neq 0$ and $|c_{kj} + q' c_{ki}| < |c_{ki}|$;
 \item $r = 0$ and $c_{kj} + q' c_{ki} = c_{ki}$.
\end{itemize}
After adding $q' \cdot c_{*i}$ to $c_{*j}$ we are either done again (first case), or 
 need to further subtract $c_{*j}$ from $c_{*i}$ to get $c_{ki} = 0$ (second case).
\end{proof}

Once $(\widetilde{A}, p_{\widetilde{A}})$ is reduced to the diagonal form, the group $\K(A, F)$ can be calculated as follows.
Each zero diagonal coefficient $r_i$ produces one summand in $\K(A, F)$ which, depending on the parity of $i$-th column, is isomorphic to either $\K(F)$ or $\Kmw(F)$, whereas
 each nonzero coefficient $r_i \neq 0$ gives one summand $\K(F)/(r_i \K(F))$ or $\Kmw(F) / ((r_i/2) I)$.

Now suppose that columns of $A$ (and hence of $\widetilde{A}$) are ordered in such a way that
 each of the first $k$ columns contains and odd entry, and the remaining $n-k$ columns consist of even entries.
The algorithm described in~\cref{lm:normal-form} allows us to present
 $\widetilde{A}$ as $p \cdot d \cdot q $ for some $q \in \E(n, \ZZ)$, $p \in \E(n(n-1)/2, \ZZ)$, $d = \mathrm{diag}(r_1, \ldots r_n)$.

It is clear that $i$-th column of $d$ is odd if and only if coefficients $q_{ij}$ are even for $k+1\leq j \leq n$
 (to see this look at everything modulo $2$).
Alternatively, $i$-th column of $d$ is odd if and only if one of the coefficients $q'_{ji}$ of the inverse matrix $q^{-1}$ is odd for some $1\leq j\leq k$.

This means, that \cite[Conjecture~9.1]{MW} is true in the special case when Westaway's matrices $\nu$, $\mu$ (which equal our $q^t$, ${q^{-1}}^t$) 
 are obtained via the algorithm described above.
Notice, however, that this criterion is not applicable for $q$ obtained from {\it arbitrary} SNF decomposition $\widetilde{A} = p d q$.
Thus, as stated in~\cite{MW}, Conjecture~9.1 is false.

%A = 
%2, -2, -3, 0
%-2, 2, -2, -4
%-1, -2, 2, 0
%0, -4, 0, 2

\printbibliography
%\begin{thebibliography}{MMMM}
%\bibitem{Li}  {\sc B.~Liehl}, {On the group $SL_2$ over orders of arithmetic type}, J. Reine Angew. Math., 323, 153--171, (1981).
%\end{thebibliography}

\end{document}

### 2017-06-17 paper.tex
Some fixes

@@
 \author {Sergey Sinchuk}
-\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
-\email {sinchukss at gmail.com}
+%\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
+%\email {sinchukss at gmail.com}
 \date {\today}
@@
 
-In this note we describe a solution of the general problem, namely we describe an algorithm for computing $\K(A, F)$ for arbitrary $A$.
+In this note we describe a solution of the general problem, namely we describe an algorithm which computues $\K(A, F)$ for arbitrary $A$.
 We also reprove some of the results of~\cite{MW} in a simplified form.
 Our algorithm is, essentially, a variant of the well-known algorithm for computing Smith normal form of a matrix.
-We also show~\cite[Conjecture 9.1]{MW} to be false as stated, and propose a way to corrected its statement.
+%We also show~\cite[Conjecture 9.1]{MW} to be false as stated, and propose a way to corrected its statement.
 
-\section{Proof of the main result}
+\subsection{Proof of the main result}
 Throughout this note $F$ denotes an arbitrary field and $A=(a_{ij})$ a generalized Cartan matrix of size $n$.
@@
 As before, we use notation $\{u, v\}_i$ for the Steinberg symbol (or cocycle) of $i$-th summand $L_i$.
-We associate to $i$-th row $c_{i*}$ of $c$ the following element of $L(p_c)$:
-\[r_{c,i}(u, v) = \{ u^{c_{i1}}, v\}_1 + \ldots + \{u^{c_{in}}, v\}_{n},\ \ u, v\in F^\times.\]
-Define $J(c)$ to be the subgroup of $L(p_c)$ generated by $r_{c, i}(u, v)$ for $1\leq i\leq m$, $u, v\in F^\times.$
-It is clear that $L(p_c)$ and $J({\widetilde{A}})$ coincide with $L$ and $J$ from the statement of~\cref{thm:mr}.
+Define $J(c)$ to be the subgroup of $L(p_c)$ generated by the following elements:
+\[ \{ u^{c_{i1}}, v\}_1 + \ldots + \{u^{c_{in}}, v\}_{n},\ \ u, v\in F^\times, 1\leq i \leq m.\]
+It is clear that $L(p_{\widetilde{A}})$ and $J({\widetilde{A}})$ coincide with $L$ and $J$ from the statement of~\cref{thm:mr}.
 
@@
   (for other operations it is similar but easier).
- Assume that $c'$ is the matrix obtained from $c$ by applying operation of type~\eqref{item:type5}.
+ Assume that $c'$ is the matrix obtained from $c$ by applying some operation of type~\eqref{item:type5}.
 
- To verify the assertion of the lemma it suffices to show that $J(c')$ is the image of $J(c)$ under an automorphism of $L(p_c)$.
+ It suffices to show that $J(c')$ is the image of $J(c)$ under an automorphism of $L(p_c)$.
  Speaking in terms of bases, it suffices to describe how the ``new'' symbols $\{u, v\}_i'$ corresponding to $c'$ 
@@
  It remains to see that $\{u, v\}_{i}^{'}$ is a Steinberg symbol.
- Although $\{u, v\}_j$ is merely a cocycle, $2k\{u, v\}_j = \{u^{2k}, v\}_j$ is a symbol (cf.~\cite[Lemma~3.2(vii)]{MW}).
+ Indeed, although $\{u, v\}_j$ is merely a cocycle, $2k\{u, v\}_j = \{u^{2k}, v\}_j$ is a symbol (cf.~\cite[Lemma~3.2(vii)]{MW}).
  Since $\{u, v\}_{i}^{'}$ is a linear combination of symbols, it is a symbol as well.
@@
 \begin{proof} 
-Recall that one of the working steps of the classical algorithm for finding Smith normal form involves
- addition of one of the two fixed columns (say, $i$-th and $j$-th ones) to another
+Recall that the classical algorithm for finding Smith normal form of a matrix involves
+ operation of addition of one of the two fixed columns (say, $i$-th and $j$-th ones) to another
  so that, unless it was zero from the start, the minimum of $|c_{ki}|$ and $|c_{kj}|$ decreases strictly 
@@
 
-To adapt the classical algorithm to the situation of matrices with parities it suffices to describe
- how the modified algorithm performs the same operation in the case when the selected columns have different parities.
-Indeed, the our elementary operations differ from the usual ones only in that they do not allow adding odd multiples of odd columns to even columns.
+To adapt the classical algorithm to our situation of matrices with parities it suffices to describe
+ how the modified algorithm performs this operation in the case when the selected columns have different parities.
+Indeed, our set of elementary operations differs from the usual one only in that
+ we do not allow adding odd multiples of odd columns to even columns.
 
@@
 
-In the case $|c_{ki}| \geq |c_{kj}|$, write $c_{ki} + q c_{kj} = r$ for some $q$ and $r$, satisfying $|r| < |c_{kj}|$.
-Using an operation of type~\eqref{item:type4} we add $q \cdot c_{*j}$ to $c_{*i}$ so that $\min(|c_{ki}|, |c_{kj}|)$ indeed decreases strictly.
+%In the case $|c_{ki}| \geq |c_{kj}|$, write $c_{ki} + q c_{kj} = r$ for some $q$ and $r$, satisfying $|r| < |c_{kj}|$.
+%Using an operation of type~\eqref{item:type4} we add $q \cdot c_{*j}$ to $c_{*i}$ so that $\min(|c_{ki}|, |c_{kj}|)$ decreases strictly.
 
-In the case $|c_{ki}| < |c_{kj}|$, write $c_{kj} + q c_{ki} = r$ for some $q$ and $r$, satisfying $|r| < |c_{ki}|$.
-If $q$ is even, we use an operation of type~\eqref{item:type5} to add $q \cdot c_{*i}$ to $c_{*j}$ and we are done again.
-Otherwise, we can choose even $q'$ equal to either $q-1$ or $q+1$ so that one of the following is true:
+We only need to consider the case $|c_{ki}| < |c_{kj}|$. Write $c_{kj} + q c_{ki} = r$ for some $q$ and $r$, satisfying $|r| < |c_{ki}|$.
+If $q$ is even, add $q \cdot c_{*i}$ to $c_{*j}$ using an operation of type~\eqref{item:type5} and 
+ notice that $\mathrm{min}(|c_{ki}|,|r|) < \mathrm{min}(|c_{ki}|,|c_{kj}|)$.
+Otherwise, choose even $q'$ equal to either $q-1$ or $q+1$ so that one of the following is true:
 \begin{itemize}
@@
 \end{itemize}
-After adding $q' \cdot c_{*i}$ to $c_{*j}$ we are either done again (first case), or 
- need to further subtract $c_{*j}$ from $c_{*i}$ to get $c_{ki} = 0$ (second case).
+In the first case after adding $q' \cdot c_{*i}$ to $c_{*j}$ we obtain the required inequality.
+In the second case we need to further subtract $c_{*j}$ from $c_{*i}$ to get $c_{ki} = 0$.
 \end{proof}
 
-Once $(\widetilde{A}, p_{\widetilde{A}})$ is reduced to the diagonal form, the group $\K(A, F)$ can be calculated as follows.
-Each zero diagonal coefficient $r_i$ produces one summand in $\K(A, F)$ which, depending on the parity of $i$-th column, is isomorphic to either $\K(F)$ or $\Kmw(F)$, whereas
+After the canonical form $(d, p_d)$ of $(\widetilde{A}, p_{\widetilde{A}})$ is found, it becomes trivial to calculate the group $\K(A, F)$.
+Each zero diagonal coefficient $r_i$ appearing in $d$ produces one summand in $\K(A, F)$ which, depending on $p_d(i)$, is isomorphic to $\K(F)$ or $\Kmw(F)$, whereas
  each nonzero coefficient $r_i \neq 0$ gives one summand $\K(F)/(r_i \K(F))$ or $\Kmw(F) / ((r_i/2) I)$.
@@
  each of the first $k$ columns contains and odd entry, and the remaining $n-k$ columns consist of even entries.
-The algorithm described in~\cref{lm:normal-form} allows us to present
- $\widetilde{A}$ as $p \cdot d \cdot q $ for some $q \in \E(n, \ZZ)$, $p \in \E(n(n-1)/2, \ZZ)$, $d = \mathrm{diag}(r_1, \ldots r_n)$.
+The algorithm given in~\cref{lm:normal-form} gives a decomposition
+ $\widetilde{A} = p \cdot d \cdot q $ for some $q \in \E(n, \ZZ)$, $p \in \E(n(n-1)/2, \ZZ)$, $d = \mathrm{diag}(r_1, \ldots r_n)$.
 
-It is clear that $i$-th column of $d$ is odd if and only if coefficients $q_{ij}$ are even for $k+1\leq j \leq n$
- (to see this look at everything modulo $2$).
-Alternatively, $i$-th column of $d$ is odd if and only if one of the coefficients $q'_{ji}$ of the inverse matrix $q^{-1}$ is odd for some $1\leq j\leq k$.
+Looking at the effect of operations \eqref{item:type2}--\eqref{item:type5} modulo $2$ one can note the following two properties of the matrix $q$:
+\begin{itemize}
+ \item $i$-th column of $d$ is odd if and only if coefficients $q_{ij}$ are even for $k+1\leq j \leq n$;
+ \item $i$-th column of $d$ is odd if and only if one of the coefficients $q'_{ji}$ of the inverse matrix $q^{-1}$ is odd for some $1\leq j\leq k$.
+\end{itemize}
 
-This means, that \cite[Conjecture~9.1]{MW} is true in the special case when Westaway's matrices $\nu$, $\mu$ (which equal our $q^t$, ${q^{-1}}^t$) 
- are obtained via the algorithm described above.
-Notice, however, that this criterion is not applicable for $q$ obtained from {\it arbitrary} SNF decomposition $\widetilde{A} = p d q$.
-Thus, as stated in~\cite{MW}, Conjecture~9.1 is false.
-
-%A = 
-%2, -2, -3, 0
-%-2, 2, -2, -4
-%-1, -2, 2, 0
-%0, -4, 0, 2
-
+In \cite{MW} M.~Westaway even conjectured that the above two properties could be used to read off from $q$ the parities of columns of $d$, and, thus, the type of summands appearing in $\K(A, F)$
+ (Westaway's matrices $\nu$, $\mu$ appearing in the statement of \cite[Conjecture~9.1]{MW} correpond to our $q$ via $\nu = q^T$, $\mu = {q^{-1}}^T$).
+While this characterization clearly works for the matrix $q$ obtained via the algorithm of~\cref{lm:normal-form},
+ it may not work for $q$ obtained via the classical algorithm for finding SNF, which ignores columns' parities.
+Thus, as stated, \cite[Conjecture~9.1]{MW} is false.
+\begin{comment}
+\begin{example}
+To produce a counterexample, start from GCM 
+ $A = \left(\begin{smallmatrix}
+ 2& -3& -2& 0\\
+-1& 2& -2& 0\\
+-2& -2& 2& -4\\
+0& 0& -4& 2\end{smallmatrix}\right)$
+  and write SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$
+\[\widetilde{A} = \left(\begin{smallmatrix}
+-1& 3& 0& 0\\
+-2& 0& 2& 0\\
+0& 0& 0& 0\\
+0& -2& 2& 0\\
+0& 0& 0& 0\\
+0& 0& -4& 4
+\end{smallmatrix} \right) = \left(\begin{smallmatrix}
+1& 0& 0& 0& 0& 0\\
+2& 1& 0& 0& 0& 0\\
+0& 0& 0& 0& 1& 0\\
+0& 1& 0& 1& 0& 0\\
+0& 0& 0& 0& 0& 1\\
+0& -2& 1& 0& 0& 0\end{smallmatrix}\right) \cdot \mathrm{diag}(-1,2,4,4) \cdot \left(\begin{smallmatrix}
+1& -3& 0& 0\\
+0& -3& 1& 0\\
+0& -3& 0& 1\\
+0& 1& 0& 0\\ \end{smallmatrix}\right) = p \cdot d \cdot q.\]
+Looking at the last 2 columns of $q$ we deduce that columns with $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd are even.
+Now take $s = t_{43}(1) \in \E(4, \ZZ)$, $t = t_{43}(-1) \ in \E(6, \ZZ)$.
+Notice that the central factor in the decomposition $\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ is still 
+ a still diagonal matrix but neither of the above two criterions is applicable to the matrix $sq$.
+\end{example}
+\end{comment}
 \printbibliography
-%\begin{thebibliography}{MMMM}
-%\bibitem{Li}  {\sc B.~Liehl}, {On the group $SL_2$ over orders of arithmetic type}, J. Reine Angew. Math., 323, 153--171, (1981).
-%\end{thebibliography}
 

### 2017-06-17 paper.tex
Minor

@@
  operation of addition of one of the two fixed columns (say, $i$-th and $j$-th ones) to another
- so that, unless it was zero from the start, the minimum of $|c_{ki}|$ and $|c_{kj}|$ decreases strictly 
- (here $k$ is some row number and $i$, $j$ are some column numbers selected by the algorithm on one if its steps).
+ so that, unless it was zero from the start, the minimum of $|c_{ki}|$ and $|c_{kj}|$ decreases strictly. 
+ Here $k$ is some row number and $i$, $j$ are some column numbers selected by the algorithm on one if its steps.
 
-To adapt the classical algorithm to our situation of matrices with parities it suffices to describe
- how the modified algorithm performs this operation in the case when the selected columns have different parities.
-Indeed, our set of elementary operations differs from the usual one only in that
+To adapt this algorithm to our situation it suffices to describe
+ how the above operation is performed in the case when $i$-th and $j$-th columns have different parities.
+Indeed, the only difference of our elementary operations from the usual ones is that
  we do not allow adding odd multiples of odd columns to even columns.
@@
 
-After the canonical form $(d, p_d)$ of $(\widetilde{A}, p_{\widetilde{A}})$ is found, it becomes trivial to calculate the group $\K(A, F)$.
-Each zero diagonal coefficient $r_i$ appearing in $d$ produces one summand in $\K(A, F)$ which, depending on $p_d(i)$, is isomorphic to $\K(F)$ or $\Kmw(F)$, whereas
- each nonzero coefficient $r_i \neq 0$ gives one summand $\K(F)/(r_i \K(F))$ or $\Kmw(F) / ((r_i/2) I)$.
+Once the canonical form $(d, p_d)$ of $(\widetilde{A}, p_{\widetilde{A}})$ is found, it becomes trivial to calculate the group $\K(A, F)$.
+Each invariant factor $r_i$ appearing in $d$ produces one summand in $\K(A, F)$ which, depending on $p_d(i)$, 
+ is isomorphic to $\K(F)/(r_i \K(F))$ or $\Kmw(F) / ((r_i/2) I)$.
 
@@
 
-In \cite{MW} M.~Westaway even conjectured that the above two properties could be used to read off from $q$ the parities of columns of $d$, and, thus, the type of summands appearing in $\K(A, F)$
- (Westaway's matrices $\nu$, $\mu$ appearing in the statement of \cite[Conjecture~9.1]{MW} correpond to our $q$ via $\nu = q^T$, $\mu = {q^{-1}}^T$).
-While this characterization clearly works for the matrix $q$ obtained via the algorithm of~\cref{lm:normal-form},
+In \cite{MW} M.~Westaway even conjectured that the above two properties could be used to read off the parities of columns of $d$ from $q$ and,
+ thus, the type of summands appearing in $\K(A, F)$
+ (Westaway's matrices $\nu$, $\mu$ appearing in the statement of \cite[Conjecture~9.1]{MW} correspond to our $q$ via $\nu = q^T$, $\mu = {q^{-1}}^T$).
+Although, as said before, this characterization works for the matrix $q$ obtained via the algorithm of~\cref{lm:normal-form},
  it may not work for $q$ obtained via the classical algorithm for finding SNF, which ignores columns' parities.

### 2017-06-21 paper.tex
Minor
Added MSC code

@@
 \author {Sergey Sinchuk}
+\keywords {$K_2$-functor, Kac---Moody groups, Smith normal form,
+ {\em Mathematical Subject Classification (2010):} 15A21, 20G44, 19C99}
 %\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
@@
 \begin{abstract} We compute $\K$-group associated to any Kac---Moody group over a field.
- The key ingredient in the computation is a variant of Smith normal form of an integer matrix.
+ The key ingredient in our computation is a variant of Smith normal form of an integer matrix.
 \end{abstract}
@@
 %\section{Introduction}
-Let $A$ be an indecomposable generalized Cartan matrix and $F$ a field.
-The aim of this note is to finish the computation of the unstable $\K$-group $\K(A, F)$ started by M.~Westaway in~\cite{MW}.
+The aim of this note is to compute the unstable $\K$-group $\K(A, F)$ for arbitrary generalized Cartan matrix $A$ and $F$ a field.
 Recall from~\cite{MR}, \cite{Ti} that the group $\K(A, F)$ is defined as the kernel of the map 
@@
 
-\subsection{Proof of the main result}
+%\subsection{Proof of the main result}
 Throughout this note $F$ denotes an arbitrary field and $A=(a_{ij})$ a generalized Cartan matrix of size $n$.
@@
 Let us first recall the precise statement of the result of Morita and Rehmann.
-Denote by $L_i$ either the Milnor group $\K(F)$ or the Milnor---Witt group $\Kmw(F)$ 
+Denote by $L_i$ either the Milnor group $\K(F)$ or the Milnor---Witt group $\Kmw(F)\cong K_2(2, F)$ 
  depending on whether or not there exists $1 \leq k \leq n$ such that the matrix coefficient $a_{ki}$ is odd.
@@
 
-In the case when all entries of $A$ are even, the coefficients $r_i$ are even as well and the group $\K(A, F)$ can be computed just as easily.
+In the case when all entries of $A$ are even, invariant factors $r_i$ are even as well and the group $\K(A, F)$ can be computed just as easily.
 %Compare the following result with~\cite[Theorem~6.1]{MW}, which is its special case.
@@
  By assumption, $c' = c \cdot t_{ij}(2k)$ for some $i$, $j$ satisfying $p_c(i)=odd$, $p_c(j)=even$.
- This operations corresponds to the following change of basis of $L(p_c)$:
+ This operation corresponds to the following change of basis of $L(p_c)$:
  \[ \{u, v\}_{i}^{'} = \{u, v\}_i - 2k\{u, v\}_j;\ \ \{u, v\}_{j}^{'} = \{u, v\}_j.\]
@@
  how the above operation is performed in the case when $i$-th and $j$-th columns have different parities.
-Indeed, the only difference of our elementary operations from the usual ones is that
+Indeed, the only difference between our elementary operations and the usual ones is that
  we do not allow adding odd multiples of odd columns to even columns.
@@
 
-Once the canonical form $(d, p_d)$ of $(\widetilde{A}, p_{\widetilde{A}})$ is found, it becomes trivial to calculate the group $\K(A, F)$.
-Each invariant factor $r_i$ appearing in $d$ produces one summand in $\K(A, F)$ which, depending on $p_d(i)$, 
- is isomorphic to $\K(F)/(r_i \K(F))$ or $\Kmw(F) / ((r_i/2) I)$.
+Combining the above two lemmas we obtain the following result.
+\begin{thm}
+If $(\widetilde{A}, p_{\widetilde{A}})$ is reduced to the canonical form $(d, p_d)$, for some $d = \mathrm{diag}(r_1, \ldots r_n)$ then
+ each invariant factor $r_i$ produces one summand in $\K(A, F)$ which, depending on $p_d(i)$, 
+ is isomorphic to $\K(F)/r_i \K(F)$ or $\Kmw(F) / (r_i/2) I$.
+\end{thm}
 
@@
 
-In \cite{MW} M.~Westaway even conjectured that the above two properties could be used to read off the parities of columns of $d$ from $q$ and,
- thus, the type of summands appearing in $\K(A, F)$
+In \cite{MW} M.~Westaway even conjectured that the above two properties could be used to determine $p_d$ from the given $q$ and,
+ thus, determine the type of summands appearing in $\K(A, F)$
  (Westaway's matrices $\nu$, $\mu$ appearing in the statement of \cite[Conjecture~9.1]{MW} correspond to our $q$ via $\nu = q^T$, $\mu = {q^{-1}}^T$).

### 2017-07-08 paper.tex
Fixes before submission

@@
 \renewcommand*{\bibfont}{\footnotesize}
+\renewcommand\thesubsection{\arabic{subsection}}
 
@@
 \DeclareMathOperator{\St}{St}
-\DeclareMathOperator{\E}{E}
+\DeclareMathOperator{\SL}{SL}
 \newcommand{\ZZ}{\mathbb{Z}}
@@
 
-\title{$\K$ of Kac---Moody groups, revisited}
+\title{A note on $\K$ of Kac---Moody groups over a field}
 \author {Sergey Sinchuk}
 \keywords {$K_2$-functor, Kac---Moody groups, Smith normal form,
- {\em Mathematical Subject Classification (2010):} 15A21, 20G44, 19C99}
-%\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
-%\email {sinchukss at gmail.com}
+ {\em Mathematical Subject Classification (2010):} 15A21, 20G44, 19C20}
+\address{Chebyshev laboratory, St. Petersburg State University, St. Petersburg, Russia}
+\email {sinchukss at gmail.com}
+\thanks {This work received financial support from the Russian Science Foundation grant 14-21-00035.}
 \date {\today}
@@
 \begin{document}   
-\begin{abstract} We compute $\K$-group associated to any Kac---Moody group over a field.
+\begin{abstract} We describe a method of computing the $\K$-group associated to any Kac---Moody group over a field.
  The key ingredient in our computation is a variant of Smith normal form of an integer matrix.
@@
 %\section{Introduction}
-The aim of this note is to compute the unstable $\K$-group $\K(A, F)$ for arbitrary generalized Cartan matrix $A$ and $F$ a field.
-Recall from~\cite{MR}, \cite{Ti} that the group $\K(A, F)$ is defined as the kernel of the map 
- $\St(A, F) \to G(A, F)$ between the corresponding Steinberg and Tits' Kac---Moody groups over $F$.
+The aim of this note is to compute the unstable $\K$-group $\K(A, F)$ for arbitrary generalized Cartan matrix $A$ and $F$ a field,
+ and thus give a complete answer to the question raised in~\cite{MW}.
+Recall from~\cite{MR}, \cite{Ti} that, by definition, the group $\K(A, F)$ is the kernel of the map 
+ $\St(A, F) \to G(A, F)$ between the corresponding Steinberg and Kac---Moody groups over $F$.
 
 In~\cite{MR} J.~Morita and U.~Rehmann described $\K(A, F)$ as a certain quotient of abelian groups, see~\cref{thm:mr} below.
-This description allows one to immediately compute $\K(A, F)$ in the case when $A$ is finite or affine (see Corollaries~4--5 of \cite{MR}).
-
-For general $A$, however, this description does not lead to an immediate answer and certain computation remains to be done.
-In~\cite{MW} this computation was made for {\it hyperbolic} GCMs, a subclass of GCMs of indefinite type. 
+Using this description, the group $\K(A, F)$ can be easily computed for finite or affine $A$ (see Corollaries~4--5 of \cite{MR}).
+For general $A$, however, this description is only indirect and one is required to do some computation in order to get an explicit answer.
+In~\cite{MW} M.~Westaway performed such computation for all {\it hyperbolic} GCMs, a subclass of GCMs of indefinite type. 
 Westaway's proof involved case-by-case analysis and, moreover, 
@@
 
-In this note we describe a solution of the general problem, namely we describe an algorithm which computues $\K(A, F)$ for arbitrary $A$.
+In this note we describe a solution of the general problem, namely we describe a method to compute $\K(A, F)$ from the given GCM $A$.
 We also reprove some of the results of~\cite{MW} in a simplified form.
-Our algorithm is, essentially, a variant of the well-known algorithm for computing Smith normal form of a matrix.
+Our method is, essentially, a variant of the well-known algorithm for computing Smith normal form of a matrix.
 %We also show~\cite[Conjecture 9.1]{MW} to be false as stated, and propose a way to corrected its statement.
 
-%\subsection{Proof of the main result}
+\subsection{Preliminaries}
 Throughout this note $F$ denotes an arbitrary field and $A=(a_{ij})$ a generalized Cartan matrix of size $n$.
@@
 
+\subsection{The main result}
 Now we turn to the case when $A$ contains columns of both types 
@@
 To solve the problem we need to invent some analogue of the fundamental theorem of finitely-generated abelian groups suitable to our sitation.
-%We solve the problem have to keep track of its columns' ``parities''.
 
@@
 \begin{enumerate}
- \item \label{item:type1} Arbitrary row operation, i.\,e. the operation that changes $b$ into $gb$ for some $g \in \E(m, \ZZ)$;
+ \item \label{item:type1} Arbitrary row operation, i.\,e. the operation that changes $b$ into $gb$ for some $g \in \SL(m, \ZZ)$;
  \item \label{item:type2} Interchanging $i$-th and $j$-th columns of $b$ 
@@
 Operations \eqref{item:type3}--\eqref{item:type5} change $b$ into $bt_{ij}(\xi)$
- for some elementary transvection matrix $t_{ij}(k)$, $1\leq i\neq j\leq n$, $k \in \ZZ$.
+ for some elementary transvection matrix $t_{ij}(k) =e+k e_{ij}$, $1\leq i\neq j\leq n$, $k \in \ZZ$.
 Notice that the matrix produced by any of the above transformations is still a matrix with parity.
@@
 The algorithm given in~\cref{lm:normal-form} gives a decomposition
- $\widetilde{A} = p \cdot d \cdot q $ for some $q \in \E(n, \ZZ)$, $p \in \E(n(n-1)/2, \ZZ)$, $d = \mathrm{diag}(r_1, \ldots r_n)$.
+ $\widetilde{A} = p \cdot d \cdot q $ for some $q \in \SL(n, \ZZ)$, $p \in \SL(n(n-1)/2, \ZZ)$, $d = \mathrm{diag}(r_1, \ldots r_n)$.
 

### 2017-08-15 paper.tex
Uncomment counterexample + cosmetics

@@
 \newtheorem{df}[lemma]{Definition} \Crefname{df}{Definition}{Definitions}
-\newtheorem{example}[lemma]{Example} \Crefname{example}{Example}{Examples}
+\newtheorem{example}{Example} \Crefname{example}{Example}{Examples}
 
@@
 \begin{document}   
-\begin{abstract} We describe a method of computing the $\K$-group associated to any Kac---Moody group over a field.
+\begin{abstract} We describe a method of computing the $\K$-group associated to any Kac--Moody group over a field.
  The key ingredient in our computation is a variant of Smith normal form of an integer matrix.
@@
 Recall from~\cite{MR}, \cite{Ti} that, by definition, the group $\K(A, F)$ is the kernel of the map 
- $\St(A, F) \to G(A, F)$ between the corresponding Steinberg and Kac---Moody groups over $F$.
+ $\St(A, F) \to G(A, F)$ between the corresponding Steinberg and Kac--Moody groups over $F$.
 
@@
 Let us first recall the precise statement of the result of Morita and Rehmann.
-Denote by $L_i$ either the Milnor group $\K(F)$ or the Milnor---Witt group $\Kmw(F)\cong K_2(2, F)$ 
+Denote by $L_i$ either the Milnor group $\K(F)$ or the Milnor--Witt group $\Kmw(F)\cong K_2(2, F)$ 
  depending on whether or not there exists $1 \leq k \leq n$ such that the matrix coefficient $a_{ki}$ is odd.
@@
 
-\begin{thm}[Morita---Rehmann] \label{thm:mr} 
+\begin{thm}[Morita--Rehmann] \label{thm:mr} 
  $\K(A, F)$ is isomorphic to the quotient $L/J$ where $L = L_1 \oplus L_2 \oplus \ldots \oplus L_n$ and 
@@
 
-Of course, the integers $r_i$ can be concretely obtained as the 
+Of course, the integers $r_i$ can be concretely obtained as
   the diagonal coefficients in the Smith normal form of the $\frac{n(n-1)}{2}\times n$ matrix $\widetilde{A}$ given by
@@
 Thus, as stated, \cite[Conjecture~9.1]{MW} is false.
-\begin{comment}
+
 \begin{example}
-To produce a counterexample, start from GCM 
+To produce a concrete counterexample, start with GCM 
  $A = \left(\begin{smallmatrix}
@@
 0& 1& 0& 0\\ \end{smallmatrix}\right) = p \cdot d \cdot q.\]
-Looking at the last 2 columns of $q$ we deduce that columns with $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd are even.
-Now take $s = t_{43}(1) \in \E(4, \ZZ)$, $t = t_{43}(-1) \ in \E(6, \ZZ)$.
+Looking at the last 2 columns of $q$ we deduce that $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd ones are even.
+Now take $s = t_{43}(1) \in \SL(4, \ZZ)$, $t = t_{43}(-1) \in \SL(6, \ZZ)$.
 Notice that the central factor in the decomposition $\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ is still 
- a still diagonal matrix but neither of the above two criterions is applicable to the matrix $sq$.
+ a diagonal matrix but neither of the above two criterions is applicable to the matrix $sq$.
 \end{example}
-\end{comment}
+
 \printbibliography

### 2017-08-15 paper.tex
Expanded final paragraph

@@
 
+We illustrate the above theorem with Example \textnumero~156 from~\cite[p.~19]{MW}.
+\begin{example}
+ Blah-blah-blah
+\end{example}
+
 Now suppose that columns of $A$ (and hence of $\widetilde{A}$) are ordered in such a way that
@@
  thus, determine the type of summands appearing in $\K(A, F)$
- (Westaway's matrices $\nu$, $\mu$ appearing in the statement of \cite[Conjecture~9.1]{MW} correspond to our $q$ via $\nu = q^T$, $\mu = {q^{-1}}^T$).
+ (Westaway's matrices $\nu$, $\mu$ appearing in the statement of \cite[Conjecture~9.1]{MW} correspond to our $q$ via $\nu = q^T$, $\mu = (q^{-1})^T$).
 Although, as said before, this characterization works for the matrix $q$ obtained via the algorithm of~\cref{lm:normal-form},
@@
 0& 0& -4& 2\end{smallmatrix}\right)$
-  and write SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$
+  and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$
 \[\widetilde{A} = \left(\begin{smallmatrix}
@@
 0& 1& 0& 0\\ \end{smallmatrix}\right) = p \cdot d \cdot q.\]
-Looking at the last 2 columns of $q$ we deduce that $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd ones are even.
-Now take $s = t_{43}(1) \in \SL(4, \ZZ)$, $t = t_{43}(-1) \in \SL(6, \ZZ)$.
-Notice that the central factor in the decomposition $\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ is still 
- a diagonal matrix but neither of the above two criterions is applicable to the matrix $sq$.
+Looking at the last 2 columns of $q$ we deduce that $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd ones are even,
+ hence $\K(A, F) \cong \Kmw/I \oplus \Kmw/2I \oplus \K(F)/4\K(F)$.
+
+Now take $s = t_{43}(1) \in \SL(4, \ZZ)$, $t = t_{43}(-1) \in \SL(6, \ZZ)$ and consider the decomposition 
+$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid Smith normal form decomposition.
+Notice that the central factor is still the diagonal matrix $\mathrm{diag}(-1,2,4,4)$ but neither of the above 
+ two criterions is able to correctly identify the type of summands appearing in $\K(A, F)$.
 \end{example}

### 2017-08-15 paper.tex
Finished writing down examples

@@
 \begin{thm}
-If $(\widetilde{A}, p_{\widetilde{A}})$ is reduced to the canonical form $(d, p_d)$, for some $d = \mathrm{diag}(r_1, \ldots r_n)$ then
+If $(\widetilde{A}, p_{\widetilde{A}})$ is reduced to Smith canonical form $(d, p_d)$, for some $d = \mathrm{diag}(r_1, \ldots r_n)$ then
  each invariant factor $r_i$ produces one summand in $\K(A, F)$ which, depending on $p_d(i)$, 
@@
 
-We illustrate the above theorem with Example \textnumero~156 from~\cite[p.~19]{MW}.
+Notice that the total numbers of odd and even columns of $d$ are the same as the corresponding numbers for $A$ and $\widetilde{A}$.
+In the simplest cases this allows one to immediately compute $\K(A, F)$ by only knowing SNF of $\widetilde{A}$.
 \begin{example}
- Blah-blah-blah
+Consider hyperbolic GCM \textnumero~156 from~\cite[p.~19]{MW}.
+ Set $A = \left(\begin{smallmatrix}
+ 2& 0& 0& -1\\
+ 0& 2& 0& -1\\
+ 0& 0& 2& -1\\
+ -2& -2& -2& 2\end{smallmatrix}\right)$.
+Clearly, $A$ has three even columns and one odd column. 
+The Smith normal form of $\widetilde{A}$ is $d=\mathrm{diag}(1,2,2,0)$.
+Notice that a diagonal coefficient of $d$ can be odd only if the corresponding column is odd.
+Thus, we get that $p_d(1)=odd$, $p_d(i)=even$ for $i>1$, hence we compute $\K(A, F)$ as $\Kmw(F)/I \oplus \Kmw(F)/I \oplus \Kmw(F)$,
+ which agrees with~\cite{MW}.
 \end{example}
@@
  each of the first $k$ columns contains and odd entry, and the remaining $n-k$ columns consist of even entries.
-The algorithm given in~\cref{lm:normal-form} gives a decomposition
+The algorithm given in~\cref{lm:normal-form} delivers SNF decomposition
  $\widetilde{A} = p \cdot d \cdot q $ for some $q \in \SL(n, \ZZ)$, $p \in \SL(n(n-1)/2, \ZZ)$, $d = \mathrm{diag}(r_1, \ldots r_n)$.
 
-Looking at the effect of operations \eqref{item:type2}--\eqref{item:type5} modulo $2$ one can note the following two properties of the matrix $q$:
+Looking at the effect of operations \eqref{item:type2}--\eqref{item:type5} modulo $2$ one can notice the following two properties of the matrix $q$:
 \begin{itemize}
@@
 Although, as said before, this characterization works for the matrix $q$ obtained via the algorithm of~\cref{lm:normal-form},
- it may not work for $q$ obtained via the classical algorithm for finding SNF, which ignores columns' parities.
+ it may not work for $q$ occurring in {\it arbitrary} SNF decomposition of $\widetilde{A}$
+ (e.\,g. the one obtained via the classical algorithm for finding SNF, which ignores columns' parities).
 Thus, as stated, \cite[Conjecture~9.1]{MW} is false.
@@
 0& 0& -4& 2\end{smallmatrix}\right)$
-  and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$
+  and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$:
 \[\widetilde{A} = \left(\begin{smallmatrix}
@@
 0& 1& 0& 0\\ \end{smallmatrix}\right) = p \cdot d \cdot q.\]
-Looking at the last 2 columns of $q$ we deduce that $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd ones are even,
+Looking at the last 2 columns of $q$ we obtain that $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd ones are even,
  hence $\K(A, F) \cong \Kmw/I \oplus \Kmw/2I \oplus \K(F)/4\K(F)$.
 
-Now take $s = t_{43}(1) \in \SL(4, \ZZ)$, $t = t_{43}(-1) \in \SL(6, \ZZ)$ and consider the decomposition 
-$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid Smith normal form decomposition.
-Notice that the central factor is still the diagonal matrix $\mathrm{diag}(-1,2,4,4)$ but neither of the above 
- two criterions is able to correctly identify the type of summands appearing in $\K(A, F)$.
+Now set $s = t_{43}(1) \in \SL(4, \ZZ)$, $t = t_{43}(-1) \in \SL(6, \ZZ)$ and consider the decomposition 
+$\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
+It remains to notice that both criterions mentioned above are unable to correctly determine the 
+ type of summands appearing in $\K(A, F)$ from the matrix $sq$.
 \end{example}

### 2017-08-15 paper.tex
Purged comments

@@
 \usepackage[hyperref=true, backend=bibtex, firstinits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}            
-%\usepackage[notref,notcite]{showkeys}
 \usepackage[matrix,arrow,curve]{xy}
@@
 
-%\newlist{lemlist}{enumerate}{1} \setlist[lemlist]{label={\rm(\arabic{lemlisti})}, ref=\thelemma.(\arabic{lemlisti}),noitemsep} \Crefname{lemlisti}{Lemma}{Lemmas}
-
 \theoremstyle{plain}
@@
 \Crefname{thm}{Theorem}{Theorems}
-%\numberwithin{equation}{section}
 
 \newtheorem{lemma}{Lemma}
-%\numberwithin{lemma}{section}
 \Crefname{lemma}{Lemma}{Lemmas}
@@
 
-\newcommand\SmallMatrix[1]{{%
-  \tiny\arraycolsep=0.3\arraycolsep\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}}
+\newcommand\SmallMatrix[1]{{\tiny\arraycolsep=0.3\arraycolsep\ensuremath{\begin{pmatrix}#1\end{pmatrix}}}}
 \DeclareMathOperator{\St}{St}
@@
 \maketitle
-%\section{Introduction}
 The aim of this note is to compute the unstable $\K$-group $\K(A, F)$ for arbitrary generalized Cartan matrix $A$ and $F$ a field,
@@
 Our method is, essentially, a variant of the well-known algorithm for computing Smith normal form of a matrix.
-%We also show~\cite[Conjecture 9.1]{MW} to be false as stated, and propose a way to corrected its statement.
 
@@
 In the case when all entries of $A$ are even, invariant factors $r_i$ are even as well and the group $\K(A, F)$ can be computed just as easily.
-%Compare the following result with~\cite[Theorem~6.1]{MW}, which is its special case.
 \begin{thm} \label{thm-even}
@@
 We also call the corresponding column $b_{*i}$ {\it odd} or {\it even} depending on the value of $p_b(i)$.
-%With this notation a matrix with parity is simply a matrix whose even columns consist of even entries.
 Notice that we make no assumptions about entries of odd columns.
@@
 \begin{proof}
- %Assertion of the lemma is not immediately obvious only for operations of type \eqref{item:type4} and \eqref{item:type5}. 
  Let us verify the assertion of the lemma, for example, for the operation of type~\eqref{item:type5}
@@
 Suppose that $i$-th column of $c$ is odd and $j$-th one is even.
-
-%In the case $|c_{ki}| \geq |c_{kj}|$, write $c_{ki} + q c_{kj} = r$ for some $q$ and $r$, satisfying $|r| < |c_{kj}|$.
-%Using an operation of type~\eqref{item:type4} we add $q \cdot c_{*j}$ to $c_{*i}$ so that $\min(|c_{ki}|, |c_{kj}|)$ decreases strictly.
 

### 2017-08-15 paper.tex
Simplified Example

@@
 \begin{example}
-To produce a concrete counterexample, start with GCM 
+To produce a counterexample, start with GCM 
  $A = \left(\begin{smallmatrix}
- 2& -3& -2& 0\\
--1& 2& -2& 0\\
--2& -2& 2& -4\\
-0& 0& -4& 2\end{smallmatrix}\right)$
+ 2& -1& -2\\
+-3& 2& -4\\
+-4& -2& 2\end{smallmatrix}\right)$
   and write down SNF decomposition of~\cref{lm:normal-form} for $\widetilde{A}$:
 \[\widetilde{A} = \left(\begin{smallmatrix}
--1& 3& 0& 0\\
--2& 0& 2& 0\\
-0& 0& 0& 0\\
-0& -2& 2& 0\\
-0& 0& 0& 0\\
-0& 0& -4& 4
+-3& 1& 0 \\
+-4& 0& 2 \\
+ 0& -2& 4
 \end{smallmatrix} \right) = \left(\begin{smallmatrix}
-1& 0& 0& 0& 0& 0\\
-2& 1& 0& 0& 0& 0\\
-0& 0& 0& 0& 1& 0\\
-0& 1& 0& 1& 0& 0\\
-0& 0& 0& 0& 0& 1\\
-0& -2& 1& 0& 0& 0\end{smallmatrix}\right) \cdot \mathrm{diag}(-1,2,4,4) \cdot \left(\begin{smallmatrix}
-1& -3& 0& 0\\
-0& -3& 1& 0\\
-0& -3& 0& 1\\
-0& 1& 0& 0\\ \end{smallmatrix}\right) = p \cdot d \cdot q.\]
-Looking at the last 2 columns of $q$ we obtain that $1$st and $4$th columns of $d$ are odd while $2$nd and $3$rd ones are even,
- hence $\K(A, F) \cong \Kmw/I \oplus \Kmw/2I \oplus \K(F)/4\K(F)$.
+ 1& 0& 0\\
+ 0& 1& 0\\
+-2& 2& 1\end{smallmatrix}\right) \cdot \mathrm{diag}(1,2,2) \cdot \left(\begin{smallmatrix}
+-3& 1& 0\\
+-2& 0& 1\\
+ 1& 0& 0 \end{smallmatrix}\right) = p \cdot d \cdot q.\]
+Looking at the last column of $q$ we get that $1$st and $3$rd columns of $d$ are odd while $2$nd one is even,
+ hence $\K(A, F) \cong \Kmw/I \oplus \K(F)/2\K(F)$.
 
-Now set $s = t_{43}(1) \in \SL(4, \ZZ)$, $t = t_{43}(-1) \in \SL(6, \ZZ)$ and consider the decomposition 
+Now set $s:= t_{32}(1)$, $t:= t_{32}(-1) \in \SL(3, \ZZ)$ and consider the decomposition 
 $\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.

### 2017-08-16 paper.tex
Minor changes in Example 2

@@
 
-In \cite{MW} M.~Westaway even conjectured that the above two properties could be used to determine $p_d$ from the given $q$ and,
- thus, determine the type of summands appearing in $\K(A, F)$
+In \cite{MW} M.~Westaway even conjectured that the above two properties are simultaneously fulfilled iff $p_d(i)=odd$, and thus, that
+ it is possible to determine the type of summands appearing in $\K(A, F)$ from the given matrix $q$
  (Westaway's matrices $\nu$, $\mu$ appearing in the statement of \cite[Conjecture~9.1]{MW} correspond to our $q$ via $\nu = q^T$, $\mu = (q^{-1})^T$).
 Although, as said before, this characterization works for the matrix $q$ obtained via the algorithm of~\cref{lm:normal-form},
- it may not work for $q$ occurring in {\it arbitrary} SNF decomposition of $\widetilde{A}$
+ it may not work for {\it arbitrary} $q$ occurring in SNF decomposition of $\widetilde{A}$
  (e.\,g. the one obtained via the classical algorithm for finding SNF, which ignores columns' parities).
@@
 $\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
-It remains to notice that both criterions mentioned above are unable to correctly determine the 
- type of summands appearing in $\K(A, F)$ from the matrix $sq$.
+Now application of Westaway's criterion to the matrix $sq$ gives incorrect answer.
+More precisely, it incorrectly determines the parity of the third column of $d$ to be even rather than odd.
 \end{example}

### 2017-08-16 paper.tex
Minor

@@
 $\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
-Now application of Westaway's criterion to the matrix $sq$ gives incorrect answer.
-More precisely, it incorrectly determines the parity of the third column of $d$ to be even rather than odd.
+Now application of Westaway's criterion to the matrix $sq$ incorrectly determines the parity of the third column of $t^{-1}ds^{-1}=d$ to be even rather than odd.
 \end{example}

### 2017-08-16 paper.tex
Improved wording

@@
 Notice that the total numbers of odd and even columns of $d$ are the same as the corresponding numbers for $A$ and $\widetilde{A}$.
-In the simplest cases this allows one to immediately compute $\K(A, F)$ by only knowing SNF of $\widetilde{A}$.
+In many cases this allows one to immediately compute $\K(A, F)$ only knowing SNF of $\widetilde{A}$.
 \begin{example}
@@
 Notice that a diagonal coefficient of $d$ can be odd only if the corresponding column is odd.
-Thus, we get that $p_d(1)=odd$, $p_d(i)=even$ for $i>1$, hence we compute $\K(A, F)$ as $\Kmw(F)/I \oplus \Kmw(F)/I \oplus \Kmw(F)$,
+Thus, we get that $p_d(1)=odd$, $p_d(i)=even$ for $i>1$, and we compute $\K(A, F)$ as $\Kmw(F)/I \oplus \Kmw(F)/I \oplus \Kmw(F)$,
  which agrees with~\cite{MW}.
@@
 Looking at the last column of $q$ we get that $1$st and $3$rd columns of $d$ are odd while $2$nd one is even,
- hence $\K(A, F) \cong \Kmw/I \oplus \K(F)/2\K(F)$.
+ hence $\K(A, F) \cong \Kmw(F)/I \oplus \K(F)/2\K(F)$.
 
@@
 $\widetilde{A} = (p t) \cdot (t^{-1} d s^{-1}) \cdot (s q)$ which is still a valid SNF decomposition.
-Now application of Westaway's criterion to the matrix $sq$ incorrectly determines the parity of the third column of $t^{-1}ds^{-1}=d$ to be even rather than odd.
+Now the application of Westaway's criterion to the matrix $sq$ incorrectly gives that the parity of the third column of $t^{-1}ds^{-1}=d$ is even rather than odd
+ and, thus, gives another $\Kmw(F)/I$ summand instead of $\K(F)/2\K(F)$.
 \end{example}

### 2017-08-24 paper.tex
Fixes as in proof

@@
 This time, however, the situation is more tricky since we cannot simply tensor out $\K(F)$ or $\Kmw(F)$.
-To solve the problem we need to invent some analogue of the fundamental theorem of finitely-generated abelian groups suitable to our sitation.
+To solve the problem we need to invent some analogue of the fundamental theorem of finitely-generated abelian groups suitable to our situation.
 
@@
 Suppose that $i$-th column of $c$ is odd and $j$-th one is even.
-
 We only need to consider the case $|c_{ki}| < |c_{kj}|$. Write $c_{kj} + q c_{ki} = r$ for some $q$ and $r$, satisfying $|r| < |c_{ki}|$.
@@
 \begin{itemize}
- \item $i$-th column of $d$ is odd if and only if coefficients $q_{ij}$ are even for $k+1\leq j \leq n$;
- \item $i$-th column of $d$ is odd if and only if one of the coefficients $q'_{ji}$ of the inverse matrix $q^{-1}$ is odd for some $1\leq j\leq k$.
+ \item $i$-th column of $d$ is odd iff coefficients $q_{ij}$ are even for $k+1\leq j \leq n$;
+ \item $i$-th column of $d$ is odd iff one of the coefficients $q'_{ji}$ of the inverse matrix $q^{-1}$ is odd for some $1\leq j\leq k$.
 \end{itemize}
 
-In \cite{MW} M.~Westaway even conjectured that the above two properties are simultaneously fulfilled iff $p_d(i)=odd$, and thus, that
+In \cite{MW} M.~Westaway even conjectured that $i$-th column of $d$ is odd iff the above two properties of $q$ are simultaneously fulfilled, and thus, that
  it is possible to determine the type of summands appearing in $\K(A, F)$ from the given matrix $q$
@@
  1& 0& 0 \end{smallmatrix}\right) = p \cdot d \cdot q.\]
-Looking at the last column of $q$ we get that $1$st and $3$rd columns of $d$ are odd while $2$nd one is even,
+Looking at the last column of $q$ we conclude that $1$st and $3$rd columns of $d$ are odd while $2$nd one is even,
  hence $\K(A, F) \cong \Kmw(F)/I \oplus \K(F)/2\K(F)$.
